---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ozbabynames

The ozbabynames package provides the dataset `ozbabynames`. This contains
popular Australian baby names by sex, state and year. 

```{r print-oz-babynames}
library(ozbabynames)
head(ozbabynames)
```

## Installation

You can install the released version of ozbabynames from github:

```{r install, eval = FALSE}
install_github("ropenscilabs/ozbabynames")
```

## Example usage

```{r example-plot}
library(ggplot2)
library(dplyr)

ozbabynames_1952_top_10 <- ozbabynames %>%
  filter(year == 1952) %>%
  group_by(sex, name) %>%
  summarise(count = sum(count)) %>%
  arrange(-count) %>%
  top_n(10) %>%
  ungroup()

ggplot(ozbabynames_1952_top_10,
       aes(x = reorder(name, count),
           y = count,
           group = sex)) +
  geom_col() +
  facet_grid(sex ~ ., 
             scales = "free_y") +
  coord_flip() +
  ylab("Count") + xlab("Name") +
  ggtitle("Top ten male and female names in 1952")
```

And let's look at the popularity of the package author names, "Rob", "Mitchell", "Nicholas", and "Jessie", as well as some similar names.

```{r explore-author-names}
author_names <- c("Robin", "Robert", "Mitchell", "Nicholas", "Jessie", "Jessica")

ozbabynames %>%
  filter(name %in% author_names) %>%
  ggplot(aes(x = year, 
             y = count,
             colour = name)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~name,
             scales = "free_y") +
  theme(legend.position = "none")

```


## Known Issues

The coverage is very
uneven, with some states only providing very recent data, and some states only
providing the top 50 or 100 names. The ACT do not provide counts, and so no ACT
data are included. South Australia has by far the best data, with full coverage
of all names back to 1944.
